Robust Digital Envelope Estimation Via Geometric Properties of an Arbitrary Real Signal

### 2020-08-24 Papers/02_Pulses_Envelope/PulsesEnvelope.tex
created curvature related images for the paper

\documentclass{article}
\usepackage{amsfonts} % \mathbb
\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[backend=biber, style=apa]{biblatex}
\usepackage{amsmath}
\DeclareMathOperator{\sign}{sign}
\bibliography{bibli}

@@

  \begin{figure}[h!]
    \centering
      \includegraphics[width=0.8\linewidth]{01Pulses.pdf}
    \caption{The grey areas encompass the simplified convex hulls of the pulses. The dashed lines mark the frontier between pseudo-cycles.}
    \label{fig:Pulses}
  \end{figure}

@@

\begin{figure}[h!]
  \centering
    \includegraphics[width=0.8\linewidth]{02AnalyticSignal.pdf}
  \caption{Envelope of a pure sinusoid modulated by a polynomial of degree 3, as obtained by the Hilbert Transform. In the first half the sinusoid is free of noise, while in the second half white gaussian noise with a standard deviation of $ 1/10 $ of the maximum amplitude of the wave was added to the base signal.}
  \label{fig:AnalyticSignal}
\end{figure}

@@

\begin{figure}[h!]
  \centering
    \includegraphics[width=0.8\linewidth]{03Frontiers.pdf}
  \caption{Positive and negative frontiers, envelope and pseudo-cycles for a fragment of piano sound. While we have only one (positive) envelope, here mirrored in the inferior space, we have two frontiers, the superior and inferior.}
  \label{fig:Frontiers}
\end{figure}

@@

As previously stated, no default discrete curvature definition exists; \textcite{2014CarrollSurvey}, for example, derives 3 such different definitions based on the approximation of a circle by an inscribed, centred e circumscribed polygon. In the context of 3d meshes, \textcite{2016VasaMultivariate} evaluates multiple estimators from a multivariate point o view.

@@

To that end we are going to apply the definition of smooth curvature as the rate of change of the unit tangent to a curve, noting that this is equivalente to that of the osculating circle \parencite{2016VasaMesh}.
The idea is to find the equivalent circle whose tangent presents the same change in direction, in the same horizontal distance, as the edge of interest.

@@

Since an edge defines only one direction, there remains the need for a reference. As we are interested in the relative curvature, it is natural to use the average direction of all vectors, $ \vec{\overline{v}} = \frac{1}{m-1} \sum_{l=0}^{m-1} \vec{v}[l] $, so as to measure the relative change of direction of each edge.

% TODO osculating circle image, average vector

% For a continuous, twice differentiable function $ y = f(x); x, y \in \mathbb{R} $, the curvature as a function of the independent variable is given by $ \kappa(x) = \frac{f''(x)}{(f'(x)^2 + 1)^{\frac{3}{2}}} $ which is also the inverse of the radius of the osculating circle tangent to the curve at $ x $. Since we are assuming smoothness of envelope in the neighbourhood of a pulse, it makes sense to approximate it with a parabola $ y(x)=ax^2+bx+c $, since a higher order polynomial would provide unnecessary complexity. Besides some characteristics of the parabola derived from its relation with Bezier curves will be useful later.

@@

>>>>

\documentclass{article}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{amsfonts} % \mathbb
\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[backend=biber, style=apa]{biblatex}
\usepackage{amsmath}
\DeclareMathOperator{\sign}{sign}
\bibliography{bibli}

@@

  \begin{figure}[ht!]
    \centering
      \includegraphics[width=0.8\linewidth]{01Pulses.pdf}
    \caption{The grey areas encompass the simplified convex hulls of the pulses. The dashed lines mark the frontier between pseudo-cycles.}
    \label{fig:Pulses}
  \end{figure}

@@

\begin{figure}[ht!]
  \centering
    \includegraphics[width=0.8\linewidth]{02AnalyticSignal.pdf}
  \caption{Envelope of a pure sinusoid modulated by a polynomial of degree 3, as obtained by the Hilbert Transform. In the first half the sinusoid is free of noise, while in the second half white gaussian noise with a standard deviation of $ 1/10 $ of the maximum amplitude of the wave was added to the base signal.}
  \label{fig:AnalyticSignal}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
    \includegraphics[width=0.8\linewidth]{03Frontiers.pdf}
  \caption{Positive and negative frontiers, envelope and pseudo-cycles for a fragment of piano sound. While we have only one (positive) envelope, here mirrored in the inferior space, we have two frontiers, the superior and inferior.}
  \label{fig:Frontiers}
\end{figure}

@@

As previously stated, no default discrete curvature definition exists; \textcite{2014CarrollSurvey}, for example, derives 3 such different definitions based on the approximation of a circle by an inscribed, centred e circumscribed polygon. In the context of 3d meshes, \textcite{2016VasaMultivariate} evaluate a range of estimators from a multivariate point o view.

@@

To that end we are going to apply the definition of smooth curvature as the rate of change of the unit tangent to a curve, noting that this is equivalent to that of the osculating circle \parencite{2016VasaMesh}.
The idea is to find the equivalent circle whose tangent presents the same change in direction, in the same horizontal distance, as the edge of interest. This approach presents the convenience of estimating the radius directly.

\begin{figure}[ht!]
  \centering
    \includegraphics[width=0.5\linewidth]{04DiscreteCurvature.pdf}
  \caption{Change of direction from horizontal, in $x_0$, until an angle of $\theta$, in $x_1$, that is equivalent to the angle between the average direction and the direction of the vector $\vec{v}[l]$ whose radius of curvature is being calculated. $x_0$ and $x_1$} correspond to the the horizontal coordinates of the tale and tip of $\vec{v}[l]$, respectively.
  \label{fig:DiscreteCurvature}
\end{figure}

@@

Since an edge defines only one direction, there remains the need for a reference. As we are interested in the relative curvature, it is natural to use the average direction of all vectors, $ \vec{\overline{v}}^\pm = \frac{1}{m-1} \sum_{l=0}^{m-1} \vec{v}[l]^\pm $, so as to measure the relative change of direction of each edge. This procedure, as well as the circles generated by it, are illustrated in figure \ref{fig:Curvatures}

\begin{figure}[ht!]
  \centering
    \includegraphics[width=0.8\linewidth]{05Curvatures.pdf}
  \caption{The equivalent circles obtained via the procedure described for the positive frontier. $\theta$, the angle between $ \vec{\overline{v}}^+$ and each of the $\vec{v}[l]^+$ is used, as is the horizontal component of each $\vec{v}[l]^+$ to obtain the radii of the circles.}
  \label{fig:Curvatures}
\end{figure}

After this procedure one obtains a set of points in $ \mathbb{R}^2 $ % TODO

\begin{figure}[ht!]
  \centering
    \includegraphics[width=0.8\linewidth]{06AvgCircle.pdf}
  \caption{The positive frontier as obtained by the use of the circle representing the average curvature of the discrete wave illustrated.}
  \label{fig:AvgCircle}
\end{figure}

@@

\subsection{Robustness}
